---
title: "Stats with R"
author: "futureCoders"
date: "10/06/2021"
output: html_document
---

R is a powerful statistical tool used frequently in science academia. Similar to Python, to use R effectively, we must use a variety of libraries.
Run the cell blocks below to install and load the necessary packages 
```{r}
install.packages("tidyverse")
install.packages("ggplot2")

```

```{r}
library("tidyverse")
library("ggplot2")
```

Today we will be analysing the happiness data. 
Please download the happiness data onto your computer from: ....
Edit and run the code cell below to load the data. 

```{r}
# first we need to set our working directory (where our files are stored)
# change the text within the "" to the path of your computer where the file is stored - for example: setwd("~/Desktop") OR above click session > set working directory > choose directory 

setwd("/path/to/my/directory")

# whilst in python we set variables using '=' in r we use '<-' 
# Here we are reading the data into a variable 
df <- read_csv("happiness_2015.csv")

# like python we can use head to look at the first few rows of the dataset
head(df)

# summary() will show you a summary of the data 
summary(df)
```

*Lets have a look at the data*
```{r}

# We can use the arrange() function to sort the data

arranged_happiness_rank <- arrange(df, happiness_rank)

arranged_happiness_rank

# We can use the select() function to look at specific columns

score_country <- select(df, happiness_score, country)

score_country

# Now have a go looking at the data in different ways:

### TYPE CODE BELOW ###



### TYPE CODE ABOVE ###
```
*Now, we need to prepare our data.*

```{r}
# first lets check for any null values

is.na(df)

# now lets prep the data




```
